### 2020-12-12 paper/sections/design.tex
minor design

\section{Detailed Design}
\label{Section: design}

@@

Initially, the agent tries different configurations $ c $ to obtain inference results image $ x_c $ from input video chunk $ x $. To obtain object detection results $ \{\vec{y}_{\rm ref}, \vec{y}_c\} $, the agent uses the choosen configuration $ c $ and the reference configuration $ x_{\rm ref} $. Comparing the two object detection results $ \{\vec{y}_{\rm ref}, \vec{y}_c\} $ and two resource consumptions $ \{\hat{s}_{\rm ref}, \hat{s}_c\} $, the agent computes the resource consumption ratio $ \Delta s = \frac{\hat{s}_c}{\hat{s}_{\rm ref}} $ and accuracy metric $ \mathcal{A}_c $.

\subsection{RL Agent Design}

@@

To address this challenges, we leverage FFmpeg \cite{FFmpeg} to extract the top $k_1$ representative images from each chunk as spatial features of video chunk. We use a pre-trained small neural network to extract the structural information embeddings $ \{e_1,e_2,...,e_{k_1}\} $ of the images to reduce the input dimension and accelerate the training procedure. This is a commonly used strategy in training a deep neural network~\cite{finetunning,finetunning2}. In this work, we use the early convolution layers of MobileNetV2~\cite{MobileNetV2} as the image feature extractor $ \mathcal{E}(\cdot) $ for its efficiency in image classification. To extract the temporal features of video chunk, we obtain $ \{\hat{e}_1,\hat{e}_2,...,\hat{e}_{{k_1}-1}\} $ by each embedding subtracting previous embedding. Besides, we record the last $k_2$ configurations $ \{c_1,c_2,...,c_{k_2}\} $. To Solve that vectors of different lengths are not conducive to input to the neural network, we use fully connected layer to transform the spatial embedding $ \{e_1,e_2,...,e_{k_1}\} $, temporal embedding $ \{\hat{e}_1,\hat{e}_2,...,\hat{e}_{{k_1}-1}\} $, and recent configuration $ \{c_1,c_2,...,c_{k_2}\} $ to the fixed length vector, similar to the work~\cite{pensieve}. We formulate the fixed length vector $ s $ as \emph{states} and the configuration $ c $ as discrete \emph{actions}.

\subsection{Reinforcement Learning-based Framework}

@@

In the training phase, the RL agent firstly using an $\epsilon-$greedy method to take some random trials to observe the environment's reaction and decreases the randomness when training afterward. In iteration $t$, we input state $s_t $ to neural network $ \phi $. The RL agent $\phi$ generates a specific configuration $c_t$. The framework processes the video chunk $x_t$ using configuration $c_t$ to inference object detection services and obtains reward $r_t$. Then the framework obtains the next video chunk $x_{t+1}$ and generates the next state $ s_{t+1} $. The framework stores transition $(s_t, c_t, r_t, s_{t+1})$ in a memory buffer $\mathcal{D}$. Especially, the transition $(s_t, c_t, r_t, s_{t+1} )$ is uesd to compute the loss function. All transitions are saved into a memory buffer $ \mathcal{D} $, and the agent learns to optimize its \emph{action} by minimizing the loss function $ L $ on a mini-batch from $ \mathcal{D} $. The training procedure would converge when the agent's randomness keeps decaying. Finally, the agent's action is based on its historical ``optimal'' experiences. The training procedure is presented in Algorithm~\ref{alg: rl-train}.

>>>>

\section{Reinforcement Learning-based Adaptive Configuration}
%\section{Detailed Design}
\label{Section: design}

@@

Initially, the agent tries different configurations $ c $ to obtain inference results $\vec{y}_c$ from input video chunk $ x $. To obtain object detection results $ \{\vec{y}_{\rm ref}, \vec{y}_c\} $, the agent uses the choosen configuration $ c $ and the reference configuration $ x_{\rm ref} $. Comparing the two object detection results $ \{\vec{y}_{\rm ref}, \vec{y}_c\} $ and two resource consumptions $ \{\hat{s}_{\rm ref}, \hat{s}_c\} $, the agent computes the resource consumption ratio $ \Delta s = \frac{\hat{s}_c}{\hat{s}_{\rm ref}} $ and accuracy metric $ \mathcal{A}_c $.

\subsection{RL Agent Design and Video's Characteristics Extraction}

@@

To address this challenges, we leverage FFmpeg \cite{FFmpeg} to extract the top $k_1$ representative images from each chunk and use a pre-trained small neural network to extract the structural Characteristics embeddings $ \{e_1,e_2,...,e_{k_1}\} $ of the images as temporal features to reduce the input dimension and accelerate the training procedure. This is a commonly used strategy in training a deep neural network~\cite{finetunning,finetunning2}. In this work, we use the early convolution layers of MobileNetV2~\cite{MobileNetV2} as the image feature extractor $ \mathcal{E}(\cdot) $ for its efficiency in image recognition. To extract the temporal features of video chunk, we obtain $ \{\hat{e}_1,\hat{e}_2,...,\hat{e}_{{k_1}-1}\} $ by each embedding subtracting previous embedding. Besides, we record the last $k_2$ configurations $ \{c_1,c_2,...,c_{k_2}\} $. To Solve that vectors of different lengths are not conducive to input to the neural network, we use fully connected layer to transform the spatial embedding $ \{e_1,e_2,...,e_{k_1}\} $, temporal embedding $ \{\hat{e}_1,\hat{e}_2,...,\hat{e}_{{k_1}-1}\} $, and recent configuration $ \{c_1,c_2,...,c_{k_2}\} $ to the fixed length vector, similar to the work~\cite{pensieve}. We formulate the fixed length vector $ s $ as \emph{states} and the configuration $ c $ as discrete \emph{actions}.

%To address this challenges, we leverage FFmpeg \cite{FFmpeg} to extract the top $k_1$ representative images from each chunk as characteristics of video chunk
\subsection{Reinforcement Learning-based Framework}

@@

In the training phase, the RL agent firstly using an $\epsilon$-greedy method to take some random trials to observe the environment's reaction and decreases the randomness when training afterward. In iteration $t$, we input state $s_t $ to neural network $ \phi $. The RL agent $\phi$ generates a specific configuration $c_t$. The framework processes the video chunk $x_t$ using configuration $c_t$ to inference object detection services and obtains reward $r_t$. Then the framework obtains the next video chunk $x_{t+1}$ and generates the next state $ s_{t+1} $. The framework stores transition $(s_t, c_t, r_t, s_{t+1})$ in a memory buffer $\mathcal{D}$. All transitions are saved into a memory buffer $ \mathcal{D} $, and the agent learns to optimize its \emph{action} by minimizing the loss function $ L $ on a mini-batch from $ \mathcal{D} $. The training procedure would converge when the agent's randomness keeps decaying. Finally, the agent's action is based on its historical ``optimal'' experiences. The training procedure is presented in Algorithm~\ref{alg: rl-train}.

### 2020-12-12 paper/sections/experiment.tex
minor design

\subsection{Experiment Setup and Configuration Selection}
\label{subsec: configuration}
We carry out real-world experiments on the object detection task (basic computer vision services) to verify our solution’s performance. We use a desktop PC (Intel Xeon E5-2650 v4 CPU) with four NVIDIA 1080ti graphic card as the server infrastructure, and simulate the environment \cite{trade-offs} with three pretrained object detection models in Tensorflow, which are SSD+ResNet152V1, FasterRCNN+ResNet50V1, FasterRCNN+InceptionResNetV2. For each model, two kinds of image resolution, which is $1024\times1024$ and $640\times640$, can be picked up. In our experiment, we set the choices space of fps as \{1, 2, 5, 10, 15, 20, 25, 30\}. We use FFmpeg \cite{ffmpeg} to switch the frame rate and image resolution, which decide which frames and in what size they should be fed to the object detection model. The configuration space comprises all possible combinations of values of these knobs, so the environment has 48 configurations in total. In the service inference, the processing video module uses CPU resources, and the object detection module uses GPU resources. In our study, we use GPU processing time as the metric of resource consumption because GPU is the dominant resource for most video processing workloads \cite{jiang2018chameleon}.In the evaluation, the processing video module needs 62s to decode 5 mins video into 9000 frames image (i.e., average CPU processing time per frame is about 0.006s), which is lower than the GPU processing time. To reduce the latency of processing video, we use different processes to carry out the processing video module and the object detection module in our experiments.

>>>>

\subsection{Experiment Setup and Configuration Selection}
\label{subsec: configuration}
We carry out real-world experiments on the object detection task (basic computer vision services) to verify our solution’s performance. We use a desktop PC (Intel Xeon E5-2650 v4 CPU) with four NVIDIA 1080ti graphic card as the server infrastructure, and simulate the environment \cite{trade-offs} with three pretrained object detection models in Tensorflow, which are SSD+ResNet152V1, FasterRCNN+ResNet50V1, FasterRCNN+InceptionResNetV2. For each model, two kinds of image resolution, which is $1024\times1024$ and $640\times640$, can be picked up. In our experiment, we set the choices space of fps as \{1, 2, 5, 10, 15, 20, 25, 30\}. We use FFmpeg to switch the frame rate and image resolution, which decide which frames and in what size they should be fed to the object detection model. The configuration space comprises all possible combinations of values of these knobs, so the environment has 48 configurations in total. In the service inference, the processing video module uses CPU resources, and the object detection module uses GPU resources. In our study, we use GPU processing time as the metric of resource consumption because GPU is the dominant resource for most video processing workloads \cite{jiang2018chameleon}.In the evaluation, the processing video module needs 62s to decode 5 mins video into 9000 frames image (i.e., average CPU processing time per frame is about 0.006s), which is lower than the GPU processing time. To reduce the latency of processing video, we use different processes to carry out the processing video module and the object detection module in our experiments.

### 2020-12-12 paper/sections/introduction.tex
minor design

A video analytics application consists of a \emph{pipeline} of several video processing modules, typically including a decoder, a selective sampling frame application, and a target detector. Such a pipeline always has multiple \emph{knobs}, such as frame rate, resolution, and model (e.g., SSD+\{MobileNet \cite{MobileNetV2}, ResNet \cite{he2016resnet}\}, FasterRCNN+\{ResNet,InceptionResNet \cite{szegedy2016inception}\}). A combination of the knob values is video analytics \emph{configuration}, and the configuration space grows \emph{exponentially} with the number of knobs, and their values \cite{jiang2018chameleon}.

>>>>

A video analytics application consists of a \emph{pipeline} of several video processing modules, typically including a decoder, a selective sampling frame application, and a target detector. Such a pipeline always has multiple \emph{knobs}, such as frame rate, resolution, and model (e.g., SSD \cite{liu2016ssd}+\{MobileNet \cite{MobileNetV2}, ResNet \cite{he2016resnet}\}, FasterRCNN \cite{ren2015faster_rcnn}+\{ResNet \cite{he2016resnet},InceptionResNet \cite{szegedy2016inception}\}). A combination of the knob values is video analytics \emph{configuration}, and the configuration space grows \emph{exponentially} with the number of knobs, and their values \cite{jiang2018chameleon}.
